---
title: "Covid-19 deaths per country in last 5 days"
author: "Thanida Prasert"
date: "December 14, 2021"
subtitle: Course_Project_Presentaton
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Instruction (1)

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

Your Shiny Application

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

The application must include the following:

1. Some form of input (widget: textbox, radio button, checkbox, ...)
2. Some operation on the ui input in sever.R
3. Some reactive output displayed as a result of server calculations
4. You must also include enough documentation so that a novice user could use your application.
5. The documentation should be at the Shiny website itself. Do not post to an external link.


## Read file 
```{r echo=TRUE}
cvd <- read.csv2("CVD.csv")
cvd
```


## ui.R 

```
library(shiny)
cvd <- read.csv2("CVD.csv")
# Use a fluid Bootstrap layout 
fluidPage(     
  titlePanel("Covid deaths per country"), 
  # Generate a row with a sidebar 
  sidebarLayout(       
    sidebarPanel(p(strong("Documentation:",style="color:Blue"), 
    a("User Info Page",href="https://github.com/Momiji5459/Course-Project-Shiny-Application-and-Reproducible-Pitch")),
    selectInput("Country", "Country:",choices=colnames(cvd[-1])), hr(), 
    helpText("Covid deaths") ), 
  
    mainPanel( 
      plotOutput("deaths")   
    ) 
  ) 
) 
```


## server.R 
```
cvd <- read.csv2("CVD.csv")
#install.packages("shiny")
function(input, output) { 
  
  # Fill in the spot we created for a plot 
  output$deaths <- renderPlot({ 
    
    # Render a barplot 
    barplot(cvd[,input$Country],  
            main=input$Country, 
            ylab="Number of covids deaths per country", 
            xlab="Day") 
  })
}
```
This is a hyperlink for Shiny Application
[Click me to see "Shiny Application"](https://tyj7ss-thanida-p.shinyapps.io/ShinyApplication/)


